A parametric system for contour parallel variable width toolpath generation

### 2019-08-10 1_intro.tex
remove thin extrusion fig
The intro si going to reer to literature more.
Using only a single image to reason for the motivation is weak
intro wedge toolpaths figure

@@

Too thin lines cannot be fabricated accurately. 
See \cref{extremal_bead_widths}.

\begin{figure}
\centering
\setlength{\figwidth}{.4\columnwidth}
%\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/intro/thin_extrusion.jpg}
%\caption{Thin}
%\end{subfigure}
\caption{
Extremal bead widths.
Bead widths from top to bottom: \SI{0.2}{\milli\meter}, \SI{0.3}{\milli\meter}, \SI{0.4}{\milli\meter}, \SI{0.5}{\milli\meter}.
Too thin lines cannot be manufactured reliably.
}
\label{extremal_bead_widths}
\end{figure}

>>>>

\begin{figure}\centering
\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_pretty.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Distributed_pretty.png}
\caption{
Toolpaths for a wedge shape using the naive offsetting approach (top) and our approach (bottom).
Red signifies overfill and blue underfill.
}
\label{intro_wedge}
\end{figure}

@@
